On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-05 manuscripts/PNAS/chazthm_pnas.tex
almost there

Before stating main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
representations.  Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$. 
% Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. 
A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %,
when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.  We also write
 supp$(\mathbf{x}) = S$ when $S$ indexes the nonzero components of $\mathbf{x}$.
Let $\mathbf{M}_j$ be the $j$th column of a matrix $\mathbf{M}$ and similarly let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$ (we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$).

@@

An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: % [*** TODO: verify this is still correct ***]
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
\end{align}
For expositional clarity, we delay defining the (explicit) constant $C_1 = C_1(\mathbf{A}, \{\mathbf{x}_i\}_{i=1}^N, E)$ until Section \ref{DUT} (\eqref{Cdef1}).  % , since it requires additional definitions not critical to the statement of our results.

@@

Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero. Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds for a value of $\gamma$ for some distribution. We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is a challenging problem in real algebraic geometry. In any case, we set $\gamma_0$ to be the smallest known such $\gamma$.

@@

Thus, choosing dictionary and sparse codes ``randomly'' generates datasets with stable sparse representations almost certainly, as long as the relevant parameters satisfy \eqref{CScondition}.

>>>>

Before stating main results, we first identify the combinatorial criteria on support sets of generating codes allowing for stable sparse 
representations.  Let $\{1, \ldots, m\}$ be denoted $[m]$, its power set $2^{[m]}$, and ${[m] \choose k}$ the set of subsets of $[m]$ of size $k$. 
% Let $\text{\rm Span}\{\mathbf{v}_1, \ldots, \mathbf{v}_\ell\}$ be the $\mathbb{R}$-linear span of vectors $\mathbf{v}_1, \ldots, \mathbf{v}_\ell$. 
A vector $\mathbf{x}$ is said to be \emph{supported} on $S \subseteq [m]$ %,
when $\mathbf{x} \in \text{\rm Span} \{\mathbf{e}_j\}_{j\in S}$, where $\mathbf{e}_j$ are the standard basis in $\mathbb R^m$.  We also write
 supp$(\mathbf{x}) = S$ when $S$ indexes the nonzero components of $\mathbf{x}$.
Let $\mathbf{M}_S$ be the submatrix formed by the columns of $\mathbf{M}$ indexed by $S$, where we set $\text{\rm Span}\{\mathbf{M}_\emptyset\} := \{\textbf{0}\}$.

@@

An important consequence of Thm.~\ref{DeterministicUniquenessTheorem} is that \eqref{def1} is guaranteed provided $\varepsilon$ in Def.~\ref{maindef} does not exceed: % [*** TODO: verify this is still correct ***]
\begin{align}\label{epsdel}
\varepsilon(\delta_1, \delta_2) := \min \left\{ \frac{\delta_1}{ C_1 }, \frac{ \delta_2 L_{2k}(\mathbf{A})}{ 1 + C_1 \left( \max_{i \in [N]} \|\mathbf{x}_i\|_1  + \delta_2 \right) } \right\}.
\end{align}
We delay defining the constant $C_1$ until Section \ref{DUT} (\eqref{Cdef1}).  % , since it requires additional definitions not critical to the statement of our results.

@@

Since $f$ is a real analytic function, having one substitution of real numbers with $f(\mathbf{A}) \neq 0$ implies that its zeroes form a set of (Borel) measure zero. Hence, almost every $n \times m$ real matrix $\mathbf{A}$ satisfies \eqref{SparkCondition} provided \eqref{CScondition} holds with a $\gamma$ for some distribution.  We set $\gamma_0$ to be the smallest known such $\gamma$. % We remark that the precise relationship between $m$, $n$, and $k$ guaranteeing that $f$ is not identically zero is a challenging problem in real algebraic geometry. In any case, we set $\gamma_0$ to be the smallest known such $\gamma$.

@@

Thus, choosing dictionary and sparse codes ``randomly'' generate data with stable sparse representations almost certainly.
% , as long as the relevant parameters satisfy \eqref{CScondition}.
